Datasheet for 'Commodity price index

### 2024-12-03 other/datasheet/datasheet_BCPI.qmd
delete unnecessary file and rename datasheet

---
title: "Datasheet for 'Commodity price index'"
subtitle: "the Bank of Canada commodity price index (BCPI)"
author: 
  - Xinqi Yue
thanks: "Code and data are available at: https://github.com/xinqiyue/exchange-rate-analysis.."
date: today
#date-format: "D MMMM YYYY"
#abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: ../../paper/references.bib
---

@@

7. *Are relationships between individual instances made explicit (for example, users' movie ratings, social network links)? If so, please describe how these relationships are made explicit.*
	The dataset includes temporal relationships between instances, as each row corresponds to a specific week.

@@

9. *Are there any errors, sources of noise, or redundancies in the dataset? If so, please provide a description.*
	- **Errors**: No explicit errors have been identified in the data set. However, errors could arise from data entry inaccuracies or revisions in the source data.

>>>>

---
title: "Datasheet for 'Commodity price index'"
subtitle: "the Bank of Canada commodity price index (BCPI)"
author: 
  - Xinqi Yue
thanks: "Code and data are available at: https://github.com/xinqiyue/exchange-rate-analysis.."
date: today
format: pdf
number-sections: true
bibliography: ../../paper/references.bib
---

@@

7. *Are relationships between individual instances made explicit (for example, users' movie ratings, social network links)? If so, please describe how these relationships are made explicit.*
	The data set includes temporal relationships between instances, as each row corresponds to a specific week.

@@

9. *Are there any errors, sources of noise, or redundancies in the dataset? If so, please provide a description.*

	- **Errors**: No explicit errors have been identified in the data set. However, errors could arise from data entry inaccuracies or revisions in the source data.
